---
title: "Functions and Automation"
author: ""
date: "2020-02-11"
output: 
  html_document
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Getting started

1. Clone your repo `appex05-[github_name]` to create a new project
   in RStudio Cloud under the STA 199 class space.

2. Configure git
      ```{r config-git-ex, eval=FALSE}
      library(usethis)
      use_git_config(user.name="your name", user.email="your email")
      ```

# Packages and Data

We'll make use of the following packages.

```{r load-packages}
library(tidyverse)
library(ggpol)
```

# Tasks

## Task 1

Write a function called `center_measures` that has one argument - `x` a 
numeric vector. The function should return the mean and median of `x`. 
Below is some sample code.

```{r task1_ex}
nums <- c(10, 5, -1, 0, 4)
c(mean(nums), median(nums))
```

```{r task1_fcn}
center_measures <- function() {
  
  
  
}
```


## Task 2

Turn the following code into a function. How many arguments does it need?
What is a good name for this function?

```{r eval=FALSE}
x / sum(x)
```

```{r task2_fcn}



```

## Task 3

```{r}
congress <- read_csv("http://www2.stat.duke.edu/courses/Spring20/sta199.002/appex/congress_long.csv")
congress
```

Write a `for` loop to compute the number of unique values in each column of
tibble `congress`. Try to stay within the `tidyverse` syntax as much as
possible.

You may find function `length()` useful. Below are some examples of it in 
action.

```{r}
length(1:10)
length(c("a", "ab", "abc", "abcd"))
length(seq(from = 2, to = 10, by = 2))
```


```{r task3_loop}



```

## Task 4

Function `plot_congress()` is similar to the function in the slides. I added
some annotation so we know the year and legislative branch.

```{r echo=FALSE}
plot_congress <- function(year, leg_branch) {
  congress %>% 
    filter(year_start == year, branch == leg_branch) %>% 
    ggplot() +
    geom_parliament(aes(seats = seats, fill = factor(party)), 
                    show.legend = FALSE, color = "black") +
    scale_fill_manual(values = c("#3A89CB", "#D65454", "#BF6FF0", "Grey"), 
                      labels = c("Dem", "GOP", "Other", "Vacant")) +
    annotate("text", x = 0, y = .5, label = paste(year, leg_branch), 
             size = 12) +
    labs(fill = "Party") +
    coord_fixed() +
    theme_void()
}
```

Run the example below to see the change that was made with `annotate()`.

```{r}
plot_congress(year = 2019, leg_branch = "house")
```

Use function `plot_congress()` to create a GIF by creating plots for each year
in object `congress` from 1993 to 2019. You'll need to put your function
call inside print and figure out the loop sequence. Once you are done,
remove chunk option `eval=FALSE`.

```{r GIF, eval=FALSE, animation.hook="gifski", interval=.75, fig.cap="Dem: blue, GOP: red, Other: purple, Vacant: grey"}
for () {
  print({
    
  })
}
```

# Slide notes





# References

1. Grolemund, G., & Wickham, H. (2020). R for Data Science. R4ds.had.co.nz. 
   Retrieved 9 February 2020, from https://r4ds.had.co.nz/
   
2. erocoar/ggpol. (2020). GitHub. Retrieved 9 February 2020, from
   https://github.com/erocoar/ggpol